---
title: "Homework 1"
author: "Kangkang Zhang"
date: "9/16/2018"
output: github_document
---

## Problem 1

Create a dataframe comprised of four different vectors:
```{r, include=FALSE}
library(tidyverse)
```

```{r Problem 1.1}

df = tibble(
  vec_unif = runif(10,0,5),
  vec_indict = I(vec_unif > 2),
  vec_char =  letters[seq(1,10)],
  vec_factor = factor(c("up","down","up","down","up","down","up","down","up","down"))
)

```

The elements and their classes are shown below:

```{r, echo = FALSE}
df
```
--------------------------

Caculate mean of each variable in the dataframe:
```{r Problem 1.2, warning = FALSE}
mean_unif = mean(df$vec_unif)
mean_indict = mean(df$vec_indict)
mean_char = mean(df$vec_char)
mean_factor = mean(df$vec_factor)
```

Generate a table of each mean value:

  Variable    |    Mean
------------- | -------------
     uniform  | `r mean_unif`
indicator  | `r mean_indict`
character  | `r mean_char`
factor  | `r mean_factor`

**Answer**: 
Uniform sample and logical vector work, while character vector and factor charactor do not work. 

*   Uniform sample are Real number which can be calculated. 

*   As for indicator variable, 1 represents TRUE and 0 represents FALSE. When indicator variable are being calculated, the numeric value is used. 

*   Character variable and factor  variable are both nominal variables, it is meaningless to calculate their means.

-----------------------------------
Convert character and factor  variable to numeric:
```{r Problem 1.3, eval = FALSE}
as.numeric(df$vec_char)
as.numeric((df$vec_factor))
```

**Result**: Charactor variable turned to be NA, while factor varible successfully converted to numeric variable.

```{r Problem 1.4, warning = FALSE}
as.numeric(as.factor(df$vec_char))
as.numeric(as.character(df$vec_factor))
```

**Result**: Character variable successfully convertd to numeric variable in the end, while factor variable failed. We can say that charactor variable cannot convert to numeric variable directly, while factor variable could.

## Problem 2