---
title: "Homework 1"
author: "Kangkang Zhang"
date: "9/16/2018"
output: github_document
---
  
## Problem 1
  
Create a dataframe comprised of four different vectors:

```{r Problem 1.1 , eval = FALSE}
library(tidyverse)
```

```{r, include = FALSE}
library(tidyverse)
```

```{r }

df1 = tibble(
  vec_unif = runif(10,0,5),
  vec_logic = I(vec_unif > 2),
  vec_char =  letters[seq(1,10)],
  vec_factor = factor(c("up","down","up","down","up","down","up","down","up","down"))
)

```

The elements and their classes are shown below:
  
```{r, echo = FALSE}
df1
```
--------------------------
  
Caculate mean of each variable in the dataframe:
```{r Problem 1.2, warning = FALSE}
mean_unif = mean(df1$vec_unif)
mean_logic1 = mean(df1$vec_logic1)
mean_char = mean(df1$vec_char)
mean_factor = mean(df1$vec_factor)
```

Generate a table of each mean value:
  
  Variable    |    Mean
------------- | -------------
uniform  | `r mean_unif`
indicator  | `r mean_logic1`
character  | `r mean_char`
factor  | `r mean_factor`

**Answer**: 
Uniform sample and logical vector work, while character vector and factor charactor do not work. 

*   Uniform sample are Real number which can be calculated. 

*   As for indicator variable, 1 represents TRUE and 0 represents FALSE. When indicator variable are being calculated, the numeric value is used. 

*   Character variable and factor  variable are both nominal variables, it is meaningless to calculate their means.

-----------------------------------

Convert character and factor  variable to numeric:

```{r Problem 1.3, eval = FALSE}
as.numeric(df1$vec_char)
as.numeric((df1$vec_factor))
```

**Result**: Charactor variable turned to be NA, while factor varible successfully converted to numeric variable.

```{r Problem 1.4, warning = FALSE}
as.numeric(as.factor(df1$vec_char))
as.numeric(as.character(df1$vec_logic1))
```

**Result**: Character variable successfully convertd to numeric variable in the end, while factor variable failed. We can say that charactor variable cannot convert to numeric variable directly, while factor variable could.

## Problem 2

Create a dataframe comprised of five different vectors:

```{r Problem 2.1}

df2 = tibble(
  x = rnorm(1000),
  y = rnorm(1000),
  vec_logic = I(x + y > 2),
  vec_num =  as.numeric(I(x + y > 2)),
  vec_factor2 = as.factor(I(x + y > 2))
)

```

--------------------------

**description**:

*  the size of the dataset: `r dim(df2)`

*  mean of x: `r mean(df2$x)`

*  the proportion of cases for which the logical vector is `TRUE`: `r mean(df2$vec_logic)`

-----------------------

Draw scatterplot of y vs x whose color points use the **logical variable**:
```{r Problem2.2}

ggplot(df2, aes(x, y)) + 
  geom_point(aes(colour = factor(df2$vec_logic))) + 
  ggtitle("y vs x using logical variable") +  
  theme(plot.title = element_text(hjust=0.5)) + 
  scale_colour_discrete(name = NULL, guide = guide_legend(reverse=TRUE), labels = c('x + y <= 2','x + y > 2'))

```

